\vskip-0.6in Trade Agreements in the Shadow of Lobbying\protect\footnote{Formerly circulated under the title ``Trade Agreements, Lobbying and Separation of Powers''}

### 2016-06-09 draft.tex
begin section on first moving leg

\subsubsection{Foreign Legislature (First Mover)}
The only strategic difference between the first mover and the second mover is that the first mover faces uncertainty about whether the other legislature will break the trade agreement.

				\begin{itemize}
					\item Legislature (equations 7 and 8 in the draft):
						\begin{equation}
							W_{ML}(\btn,\ga(e_b,\ve_b)) > W_{ML}\left(\bta,\ga(e_b,\ve_b)\right)
							\label{eq:lwcg}
						\end{equation}
						becomes
						\[ 
						  W_{ML}(\btn,\ga(e_b,\ve_b)) > b^* W_{ML}\left(\btn,\ga(e_b,\ve_b)\right) + (1-b^*) W_{ML}\left(\bta,\ga(e_b,\ve_b)\right)
						\]
						This can be arranged as 
						\[ 
						  W_{ML}(\btn,\ga(e_b,\ve_b)) - W_{ML}(\bta,\ga(e_b,\ve_b)) > b^* \left[ W_{ML}\left(\btn,\ga(e_b,\ve_b)\right) - W_{ML}\left(\bta,\ga(e_b,\ve_b)\right) \right]
						\]
						This has the interesting structure that it is always true when (\ref{eq:lwcg}) is true, and is false whenever (\ref{eq:lwcg}) is false. So all the same results go through after modifying the objective function for the legislature
					\item Lobby: objective function was
					  \[
							\max_{e_b} b(e_b,\bta) \left[\pi(\tau^n) - e_n \right] + [1 - b(e_b,\bta)] \pi(\tau^a) - e_b
						\]
						Now it's 
						\begin{multline*}
							\max_{e_b} \left\{ b(e_b,\bta) + b^*(1-b(e_b,\bta)) \right\} \left[\pi(\tau^n) - e_n \right] + \\
							[1 - b(e_b,\bta) - b^* + b(e_b,\bta) b^*] \pi(\tau^a) - e_b
						\end{multline*}
						So the first order condition becomes 
						\begin{equation}
							\frac{\partial b(e_b,\bta)}{\partial e_b} \left[1-b^*(e_b^*,\bta)\right] \left[ \pi(\tau^n) -e_n - \pi(\tau^a) \right] = 1 
						\end{equation}
						I believe that only Result 2 is in peril. A new term is added in the numerator (the denominator just gets a $(1-b^*)$; by the product rule, there are two terms after differentiating. The first is negative, the second is positive but can be combined with the pre-existing second term which just becomes less negative now. Should write all this up.
				\end{itemize}

>>>>

\subsubsection{Foreign Legislature (First Mover)}
The only strategic difference between the first-moving legislature and the second moving legislature is that the first mover faces uncertainty about whether the other legislature will break the trade agreement. In constructing the break probability for the foreign legislature $b^*(e_b^*,\bta)$, Expression~\ref{eq:lwcg} becomes
		\[ 
		  W_{ML}^*(\btn,\ga(e_b^*,\ve_b^*)) > b(e_b,\bta) W_{ML}^*\left(\btn,\ga(e_b^*,\ve_b^*)\right) + \left[1-b(e_b,\bta)\right] W_{ML}^*\left(\bta,\ga(e_b^*,\ve_b^*)\right)
		\]
	This inequality determining when the foreign legislature prefers to break the trade agreement can be arranged as 
		\begin{equation}
						  W_{ML}^*(\btn,\ga(e_b^*,\ve_b^*)) - W_{ML}^*(\bta,\ga(e_b^*,\ve_b^*)) > b(e_b,\bta) \left[ W_{ML}^*\left(\btn,\ga(e_b^*,\ve_b^*)\right) - W_{ML}^*\left(\bta,\ga(e_b^*,\ve_b^*)\right) \right]
			\label{eq:lwcg_for}
		\end{equation}
	Given symmetry, Expression~\ref{eq:lwcg_for} is true precisely when Expression~\ref{eq:lwcg} is true and false whenever Expression~\ref{eq:lwcg}) is false. 
				\begin{itemize}

					\item	So all the same results go through after modifying the objective function for the legislature
					\item Lobby: objective function was
					  \[
							\max_{e_b} b(e_b,\bta) \left[\pi(\tau^n) - e_n \right] + [1 - b(e_b,\bta)] \pi(\tau^a) - e_b
						\]
						Now it's 
						\begin{multline*}
							\max_{e_b} \left\{ b(e_b,\bta) + b^*(1-b(e_b,\bta)) \right\} \left[\pi(\tau^n) - e_n \right] + \\
							[1 - b(e_b,\bta) - b^* + b(e_b,\bta) b^*] \pi(\tau^a) - e_b
						\end{multline*}
						So the first order condition becomes 
						\begin{equation}
							\frac{\partial b(e_b,\bta)}{\partial e_b} \left[1-b^*(e_b^*,\bta)\right] \left[ \pi(\tau^n) -e_n - \pi(\tau^a) \right] = 1 
						\end{equation}
						I believe that only Result 2 is in peril. A new term is added in the numerator (the denominator just gets a $(1-b^*)$; by the product rule, there are two terms after differentiating. The first is negative, the second is positive but can be combined with the pre-existing second term which just becomes less negative now. Should write all this up.
				\end{itemize}
